---
title: "Compute REFLIN tolerance times"
author: "John Minter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette

vignette: >
  %\VignetteIndexEntry{Compute REFLIN tolerance times}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE,
  comment = NA,
  fig.align = "centre",
  fig.height = 4,
  fig.width = 7.25,
  message = FALSE,
  warning = FALSE,
  error = FALSE)
```

# Set up for the analysis

Set the paths and constants that we need

```{r setPaths}
library(rpenepma)
library(ggplot2)
e0 <- 4 # kV
sim_nam  <- "Al-100-nm-on-Fe"
out_ti   <- sprintf("%s-%gkV", sim_nam, e0)

rd_path <- system.file("extdata", "Al-100nm-on-Fe-4kV-1000ch",
                       "al_100nm_on_fe_4kv.rda", package = "rpenepma")
int_fi  <- system.file("extdata", "Al-100nm-on-Fe-4kV-1000ch",
                       "pe-intens-01.dat", package = "rpenepma")
spc_fi  <- system.file("extdata", "Al-100nm-on-Fe-4kV-1000ch",
                       "pe-spect-01.dat", package = "rpenepma")
```


Load our REFLIN data and print the head.

```{r loadRefHead}
load(rd_path)
print(head(al_100nm_on_fe_4kv, 5))
```

Print the tail

```{r printRefTail}
print(tail(al_100nm_on_fe_4kv, 5))
```

## Plot the simulation time (sec) as a function of relative uncertainty

```{r plot_tol_vs_time}
tol_vs_time_plt <- ggplot(al_100nm_on_fe_4kv,
                          aes(x = rel_unc, y = sim_time_sec)) +
                   geom_point() +
                   xlab("relative uncertainty") +
                   ylab("simulation time [sec]") +
                   ggtitle("100 nm Al on Fe at 4 kV") +
                   theme(axis.text=element_text(size=12),
                         axis.title=element_text(size=12),
                         plot.title=element_text(hjust = 0.5))
                   

print(tol_vs_time_plt)
```


## Plot the simulation time (sec) as a function of the inverse relative uncertainty

```{r plot_inv_rel_unc_vs_time}
inv_rel_unc_vs_time_plt <- ggplot(al_100nm_on_fe_4kv,
                                  aes(x = 1/rel_unc,
                                      y = sim_time_sec)) +
                                  geom_point() +
                                  stat_smooth(method = 'lm',
                                              formula = y ~ I(x^2) + 0,
                                              aes(' ' = 'darkblue'),
                                              se = FALSE) +
                                  xlab("inverse relative uncertainty") +
                                  ylab("simulation time [sec]") +
                                  ggtitle("100 nm Al on Fe at 4 kV") +
                                  theme(axis.text=element_text(size=12),
                                        axis.title=element_text(size=12),
                                        plot.title=element_text(hjust = 0.5))

print(inv_rel_unc_vs_time_plt)
```

## Fit a second order polynomial to the system

Model the system as a second order polynomial with a zero intercept.

```{r polyModel}
x <- 1.0 / al_100nm_on_fe_4kv$rel_unc
y <- al_100nm_on_fe_4kv$sim_time_sec

poly_mod <- lm(y ~ I(x^2) + 0)
pander(summary(poly_mod))

```

So for a `0.2` relative uncertainty, we predict a simulation time
of

```{r}
coef <- summary(poly_mod)$coefficients
x <- 1.0/0.2
y <- coef[1] * x*x / (60*60)
ans <- sprintf("%.1f hrs", y)
cat("predicted value for tolerance = 0.2:", ans)
```

and for a `0.02` relative uncertainty, we predict a simulation time
of


```{r}
x <- 1.0/0.02
y <- coef[1] * x*x / (60*60)
ans <- sprintf("%.1f hrs", y)
cat("predicted value for tolerance = 0.02:", ans)
```

```{r}
hrs <- max(al_100nm_on_fe_4kv$sim_time_sec)/(60*60)
cat("measured value for tolerance = 0.02:", hrs, "hrs")
```

# Process the spectra data

## Load the raw data

```{r loadSpectraData}
spc_tib <- penepma_read_raw_data(spc_fi)
rownames(spc_tib) <- c()
```

## Plot the spectrum on a log scale


```{r plotLogIntensSpectrum, fig.width = 8, warning = FALSE}
subset <- spc_tib %>%
          filter(keV < 2.0)
plt <- ggplot(subset, aes(x = keV, y = pd.mu)) +
       geom_line() + 
       scale_x_continuous(breaks = seq(from = 0, to = e0, by = 1)) +
       scale_y_log10() +
       xlab(label = "X-ray energy [keV]") +
       ylab(label = "log(probability density)") +
       # (1/(eV*sr*electron)") +
       ggtitle(out_ti) +
       theme(axis.text = element_text(size = 12),
             axis.title = element_text(size = 12),
             # center the title
             plot.title = element_text(hjust = 0.5))
       
print(plt)
```

## Plot the spectrum on a linear scale


```{r plotLinIntensSpectrum, fig.width = 8, warning = FALSE}
plt <- ggplot(subset, aes(x = keV, y = pd.mu)) +
       geom_line() + 
       scale_x_continuous(breaks = seq(from = 0, to = 2, by = 0.25)) +
       scale_y_continuous() +
       xlab(label = "X-ray energy [keV]") +
       ylab(label = "Probability density") +
       # (1/(eV*sr*electron)") +
       ggtitle(out_ti) +
       theme(axis.text = element_text(size = 12),
             axis.title = element_text(size = 12),
             # center the title
             plot.title = element_text(hjust = 0.5))
       
print(plt)
```

