---
title: "Get the maximum intensity for selected elements from penepma"
author: "John Minter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get the maximum intensity for selected elements from penepma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA
)
```

Our objective is to compute the maximum intensity from selected elements
from a penepma simulation of C-coated EagleXG glass. We have two
functions: one reports the **maximum primary intensity** and the 
second reports the **maximum total intensity**.

## Load the intensity file

First we get our example file stored in the package.

```{r getPath}
spcPath <- system.file("extdata", "pe-intens-01.dat", package = "rpenepma")
spcPath
```

## Convert the data to a convenient form 

We create a tibble using the `penepma_get_intensities` function.


```{r loadTibble, message=FALSE}
library(rpenepma)
tib <- penepma_get_intensities(spcPath)
```

## Ask some key questions

1. How many transitions do we have? 

```{r numTrans, message=FALSE}
print(nrow(tib))
```

2. What values are reported.

```{r valuesRep, message=FALSE}
print(names(tib))
```

Now we can make some useful computations...

## Compute the maximum primary intensities for key elements


```{r calcPrimary, message=TRUE}
C.p  <- penepma_get_max_primary_intensity_z(tib, 6)
Si.p <- penepma_get_max_primary_intensity_z(tib, 14)
O.p  <- penepma_get_max_primary_intensity_z(tib, 8)
Ca.p <- penepma_get_max_primary_intensity_z(tib, 20)
```

## Compute the maximum total intensities for key elements

```{r calcTotal, message=TRUE}
C.t <- penepma_get_max_total_intensity_z(tib, 6)
Si.t <- penepma_get_max_total_intensity_z(tib, 14)
O.t <- penepma_get_max_total_intensity_z(tib, 8)
Ca.t <- penepma_get_max_total_intensity_z(tib, 20)
```

## Create a summary report with two tables

First, the primary intensity. Note that `penepma` does not report
the `SNR` for the transitions, but we can easily compute and append
the value. The `*_intensity_z` functions do this.

```{r primInt, message=TRUE}
primInt <- dplyr::bind_rows(C.t, Si.t, O.t, Ca.t)
print(primInt)
```

Prepend a sample ID

```{r addSIDpi, message=TRUE}
primInt <- prepend_sample_id_max_int_tib(primInt, "Eagle-XG")
print(primInt)

```
Followed by the total intensity

```{r totalInt, message=TRUE}
totInt <- dplyr::bind_rows(C.t, Si.t, O.t, Ca.t)
print(totInt)
```

Prepend a sample ID

```{r addSIDti, message=TRUE}
totInt <- prepend_sample_id_max_int_tib(totInt, "Eagle-XG")
print(totInt)

```
