---
title: "Get the maximum intensity for selected elements from penepma"
author: "John Minter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get the maximum intensity for selected elements from penepma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA
)
```

Our objective is to compute the maximum intensity from selected elements
from a penepma simulation of C-coated EagleXG glass. We have two
functions: one reports the **maximum primary intensity** and the 
second reports the **maximum total intensity**.

## Load the intensity file

First we get our exemplar file.

```{r getPath}
spcPath <- system.file("extdata", "pe-intens-01.dat", package = "rpenepma")
spcPath
```

Then we create a tibble using the `penepma_get_intensities` function

```{r loadTibble, message=FALSE}
library(rpenepma)
tib <- penepma_get_intensities(spcPath)
print(summary(tib))
```

Now compute the maximum primary intensity for C


```{r calcCarbonPrimary, message=TRUE}
C.p <- penepma_get_max_primary_intensity_z(tib, 6)
print(C.p)
```
and the maximum total intensity

```{r calcCarbonTotal, message=TRUE}
C.t <- penepma_get_max_total_intensity_z(tib, 6)
print(C.t)
```



Next, compute the maximum primary intensity for Si

```{r calcSiliconPrimary, message=TRUE}
Si.p <- penepma_get_max_primary_intensity_z(tib, 14)
print(Si.p)
```

Then compute the maximum total intensity for Si

```{r calcSiliconTotal, message=TRUE}
Si.t <- penepma_get_max_total_intensity_z(tib, 14)
print(Si.t)
```

Next, compute the maximum primary intensity for O

```{r calcOxygenPrimary, message=TRUE}
O.p <- penepma_get_max_primary_intensity_z(tib, 8)
print(O.p)
```

Then, compute the maximum total intensity for O

```{r calcOxygenTotall, message=TRUE}
O.t <- penepma_get_max_total_intensity_z(tib, 8)
print(O.t)
```


Finally, compute the maximum primary intensity for Ca

```{r calcCalciumPrimary, message=TRUE}
Ca.p <- penepma_get_max_primary_intensity_z(tib, 20)
print(Ca.p)
```

and the maximum total intensity for Ca

```{r calcCalciumTotal, message=TRUE}
Ca.t <- penepma_get_max_total_intensity_z(tib, 20)
print(Ca.t)
```

