---
title: "Plot Penepma Spectra"
author: "John Minter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot Penepma Spectra}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA
)
```

Our objective is to convert an output spectrum from a Monte Carlo
simulation using PENEPMA into a R dataframe for analysis and other
processing.


## Load a spectrum

First we get our exemplar file.

```{r}
spcPath <- system.file("extdata", "pe-spect-01.dat", package = "rpenepma")
spcPath
```

Then we create an R dataframe using the `penepma_read_raw_data` function.

```{r, message=FALSE}
library(rpenepma)
library(pander)
library(ggplot2)

df <- penepma_read_raw_data(spcPath)
rownames(df) <- c()

pander(head(df))
```
and the tail

```{r, message=FALSE}
pander(tail(df))
```

```{r}
pander(summary(df))
```


Now we are ready to plot the spectrum. There is a very large dynamic
range for both the **probability density** and the **uncertainty**.
Penepma sets a lower limit for data at **1.0e-35**. Missing values are
set to zero. We want to remove values from the dataframe that are
below a useful limit. We do this below and plot a copy of the 
dataframe that is limited to the useful values.

```{r, fig.width=7, warning=FALSE}
plt <- ggplot(df, aes(x = keV, y = mu)) +
       geom_line() + 
       scale_x_continuous(breaks = seq(from = 0, to = 15, by = 1),
                          limits = c(0,15)) +
       scale_y_log10(limits = c(0.001, 1.0e+4)) +
       xlab(label="X-ray energy [keV]") +
       ylab(label="probability density") +
       # (1/(eV*sr*electron)") +
       ggtitle('PENEPMA simulation of Corning EagleXG glass at 15 kV') +
       theme(axis.text=element_text(size=12),
             axis.title=element_text(size=12),
             # center the title
             plot.title = element_text(hjust = 0.5))
       
print(plt)

```
